Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-13 manuscript/climate_sensitivity_SI.Rmd
update to new phytologist citation style (.csl)

---
title: ""
author: ""
output:
  pdf_document:
    fig_caption: yes
bibliography: ["packages.bib"]
biblio-style: apalike
header-includes:
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{setspace}\onehalfspacing
- \captionsetup[figure]{labelformat=empty}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
---

>>>>

---
title: ""
author: ""
output:
  pdf_document:
    fig_caption: yes
bibliography: ["packages.bib"]
biblio-style: apalike
csl: new-phytologist.csl
header-includes:
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{setspace}\onehalfspacing
- \captionsetup[figure]{labelformat=empty}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
---

### 2020-07-13 manuscript/climate_sensitivity_draft.Rmd
update to new phytologist citation style (.csl)

---
title: ""
author: ""
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
biblio-style: "apalike"
csl: apa.csl
header-includes:
- \usepackage{setspace}\onehalfspacing
- \usepackage{lineno}
- \linenumbers
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

@@

For each drought year, we calculated drought resistance ($Rt$) as the ratio of basal area increment ($BAI$) during drought to the mean $BAI$ over the five years preceding the drought [@lloret_components_2011]. Thus, $Rt$ values <1 and >1 indicate growth reductions and increases, respectively. Because the $Rt$ metric could be biased by directional pre-drought growth trends, we also tried an intervention time series analysis (ARIMA, [@R-forecast]) that predicted mean drought-year growth based on trends over the past **10** years and used this value in place of the five-year mean in calculations of resistance ($Rt_{ARIMA}$= observed $BAI$/ predicted $BAI$). Because $Rt$ tended to produce more reasonable estimates than $Rt_{ARIMA}$ when there was a large difference between these metrics, we selected $Rt$ as our focal metric, presenting parallel results for $Rt_{ARIMA}$ in the Supplementary Info. We focus exclusively on drought resistance ($Rt$ or $Rt_{ARIMA}$), and not on the resilience metrics described in @lloret_components_2011, because (1) we would expect resilience to be controlled by a different set of mechanisms, and (2) the findings of *[DeSoto et al. (2020)](https://www.nature.com/articles/s41467-020-14300-5)* suggest that $Rt$ is a more important drought response metric for angiosperms.

>>>>

---
title: ""
author: ""
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
biblio-style: "apalike"
csl: new-phytologist.csl
header-includes:
- \usepackage{setspace}\onehalfspacing
- \usepackage{lineno}
- \linenumbers
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

@@

For each drought year, we calculated drought resistance ($Rt$) as the ratio of basal area increment ($BAI$) during drought to the mean $BAI$ over the five years preceding the drought [@lloret_components_2011]. Thus, $Rt$ values <1 and >1 indicate growth reductions and increases, respectively. Because the $Rt$ metric could be biased by directional pre-drought growth trends, we also tried an intervention time series analysis (ARIMA, [@R-forecast]) that predicted mean drought-year growth based on trends over the past ten years and used this value in place of the five-year mean in calculations of resistance ($Rt_{ARIMA}$= observed $BAI$/ predicted $BAI$). Because $Rt$ tended to produce more reasonable estimates than $Rt_{ARIMA}$ when there was a large difference between these metrics, we selected $Rt$ as our focal metric, presenting parallel results for $Rt_{ARIMA}$ in the Supplementary Info. We focus exclusively on drought resistance ($Rt$ or $Rt_{ARIMA}$), and not on the resilience metrics described in @lloret_components_2011, because (1) we would expect resilience to be controlled by a different set of mechanisms, and (2) the findings of *[DeSoto et al. (2020)](https://www.nature.com/articles/s41467-020-14300-5)* suggest that $Rt$ is a more important drought response metric for angiosperms.

### 2020-07-13 manuscript/tables&figures.Rmd
update to new phytologist citation style (.csl)

---
title: ""
author: ""
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
biblio-style: "apalike"
csl: apa.csl
header-includes:
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \usepackage{setspace}\onehalfspacing
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

>>>>

---
title: ""
author: ""
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: ["book.bib",  "packages.bib"]
biblio-style: "apalike"
csl: new-phytologist.csl
header-includes:
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \usepackage{setspace}\onehalfspacing
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---
